---
title: "ANLY503 Assignment5"
output:
  html_document:
    #toc: true
    self_contained: no
    #toc_depth: 6
---

### Altair

Question 1: 
* For each household, which appliance/period in a week/day used the most electricity? 

This plot shows the consumption of 3 households by weekdays, appliances and different time period in a day, in billions. 

The techniques used are detail-on-demand, panning, tooltip. By clicking one bar, we can elaborate any parts with details. For example, choosing bar with different color will result in the display of different households. Since we use `consumption` and `house` in both plots, make them interactive will be the best choice due to convenience. 

Rationale:
By this plot, we can explore the different consumption details by weekdays/time periods daily and appliances. Since bar plots will show the difference clearly, those are chosen as below. 

Alternatives:
Pie chart/line plot could make it better but unfortunately, pie charts are not supported in Altair in python.

Answer:
To answer the question 1, we could see house 4 used Freezer the most, and consumed the most when its Friday in a week, and at night in a day. House 5 used Fridge the most, and consumed the most when its Friday in a week, and at night in a day. House 6 used Entertainment (TV/stereo) the most, and consumed the most when its Friday in a week, and at night in a day.

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.cap="A simple plot"}
htmltools::includeHTML('./docs/altair.html')
```


### Plotly
Question 2: "Which are the abnormal time period in house 4 based on their daily consumption?"

This plot is a density plot by `date` and `appliances` of house 4. Since from the first plot, we see house 4 consume more electricity in millions than the other two households, we now zoom in and focus on house 4 with question 2. 

Same with the first plot, the techniques used are demand-on-details, panning and tooltip. This one shows daily `consumption` by `appliances` with details. Also, by clicking the legend, for example "Freezer" once, this category will be isolated, so we can subtract the abnormal / extreme category and explore others. The time slot at the bottom gives a time measure of the whole period. We can easily move forward / backward with it. 

Alternatives:
As a time-series data set, line plot and density plot are the most appropriate one to show the details daily.

Answer:
We find out that from late Dec. 2012 to early Jan. 2013, house 4 had abnormal consumption, especially on 'Freezer'.

```{r echo=FALSE, message=FALSE, warning=FALSE}
htmltools::includeHTML('./docs/plotly.html')
```


